CommonMind Consortium: DLPFC

### 2020-09-21 combined_analysis/diff.networks.Rmd
Update diff networks

# Null permuations
```{r diff.networks.perm, eval=FALSE}

@@

	dynamicMods = cutreeDynamic(hcl, distM=C.diff.discovery, minClusterSize = minClusterSize, deepSplit=2)

@@

	# Hypothesis testing         
	df_test = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors, METADATA, variable, useSLED=FALSE)

@@

```{r perm.results, fig.width=5, eval=FALSE}
p = df_test$P.Value[df_test$Cohort=="MSSM-Penn-Pitt"]
# print(1 - qvalue(p)$pi0)
hist(p, main="P-values under the null in the discovery cohort", xlab="p-value")

@@

# Null network
```{r diff.networks.null, eval=FALSE}

@@

dynamicMods = cutreeDynamic(hcl, distM=C.diff.discovery, minClusterSize = minClusterSize, deepSplit=2)

# Hypothesis testing         
df_test_null = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors, METADATA, variable, useSLED=FALSE) 
```

```{r recalibrate.null, eval=FALSE}
df_test_recal = apply_permutation_null( df_test_null )

@@

res = pickSFT( diff.net.Sex )

ggplot(res, aes(Power, -sign(slope)*SFT.R.sq, color=paste(Cohort, Dataset, sep=' - '))) + geom_point() + theme_bw() + theme(aspect.ratio=1,  plot.title = element_text(hjust = 0.5)) + xlab("Soft Threshold (power)") + ylab("Scale Free Topology Model Fit,signed R^2") + ggtitle("Scale independence")

@@

dynamicMods = cutreeDynamic(hcl, distM=C.diff.discovery, minClusterSize = minClusterSize, deepSplit=2)

dynamicColors.Sex = labels2colors( dynamicMods )
tab = table(dynamicColors.Sex)
hist(tab, xlab="Cluster size")
```

```{r testing}
# Hypothesis testing         
df_test.Sex = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors.Sex, METADATA, variable, .3, 20)
```

@@

res = pickSFT( diff.net.Dx )

ggplot(res, aes(Power, -sign(slope)*SFT.R.sq, color=paste(Cohort, Dataset, sep=' - '))) + geom_point() + theme_bw() + theme(aspect.ratio=1,  plot.title = element_text(hjust = 0.5)) + xlab("Soft Threshold (power)") + ylab("Scale Free Topology Model Fit,signed R^2") + ggtitle("Scale independence")

@@

res = pickSFT( net.Dx_Sex )

ggplot(res, aes(Power, -sign(slope)*SFT.R.sq, color=paste(Cohort, Dataset, sep=' - '))) + geom_point() + theme_bw() + theme(aspect.ratio=1,  plot.title = element_text(hjust = 0.5)) + xlab("Soft Threshold (power)") + ylab("Scale Free Topology Model Fit,signed R^2") + ggtitle("Scale independence")

>>>>

# Null permuations
```{r diff.networks.perm}

@@

	# dynamicMods = cutreeDynamic(hcl, distM=C.diff.discovery, minClusterSize = minClusterSize, deepSplit=2)
	dynamicMods = cutree(hcl, k=200)

@@

	# Hypothesis testing         
	df_test = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors, METADATA, variable, useSLED=TRUE, .5, 20)

@@

```{r perm.results, fig.width=5}
p = df_test$P.Value[df_test$Cohort=="MSSM-Penn-Pitt"]
# print(1 - qvalue(p)$pi0)
hist(p, main="P-values under the null in the discovery cohort", xlab="p-value")

@@

# Null network
```{r diff.networks.null}

@@

# dynamicMods = cutreeDynamic(hcl, distM=C.diff.discovery, minClusterSize = minClusterSize, deepSplit=2)
dynamicMods = cutree(hcl, k=200)

dynamicColors = labels2colors(dynamicMods, colorSeq=colors())
tab = table(dynamicColors)

# Hypothesis testing         
df_test_null = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors, METADATA, variable, useSLED=TRUE, .5, 20) 
```

```{r recalibrate.null}
df_test_recal = apply_permutation_null( df_test_null )

@@

# res = pickSFT( diff.net.Sex )

# ggplot(res, aes(Power, -sign(slope)*SFT.R.sq, color=paste(Cohort, Dataset, sep=' - '))) + geom_point() + theme_bw() + theme(aspect.ratio=1,  plot.title = element_text(hjust = 0.5)) + xlab("Soft Threshold (power)") + ylab("Scale Free Topology Model Fit,signed R^2") + ggtitle("Scale independence")

@@

# dynamicMods = cutreeDynamic(hcl, distM=C.diff.discovery, minClusterSize = minClusterSize, deepSplit=2)
dynamicMods = cutree(hcl, k=200)

# find k so that max size of cluster is
# k = sapply( seq(100, 1000, by=10), function(k) max(table(cutree(hcl, k=k))))

dynamicMods = cutree(hcl, k=200)

dynamicColors.Sex = labels2colors( dynamicMods, colorSeq=colors() )
tab = table(dynamicColors.Sex)
hist(tab, xlab="Cluster size")
```

```{r testing}
# Hypothesis testing         
df_test.Sex = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors.Sex, METADATA, variable, useSLED=TRUE, .5, 20)
```

@@

# res = pickSFT( diff.net.Dx )

# ggplot(res, aes(Power, -sign(slope)*SFT.R.sq, color=paste(Cohort, Dataset, sep=' - '))) + geom_point() + theme_bw() + theme(aspect.ratio=1,  plot.title = element_text(hjust = 0.5)) + xlab("Soft Threshold (power)") + ylab("Scale Free Topology Model Fit,signed R^2") + ggtitle("Scale independence")

@@

# res = pickSFT( net.Dx_Sex )

# ggplot(res, aes(Power, -sign(slope)*SFT.R.sq, color=paste(Cohort, Dataset, sep=' - '))) + geom_point() + theme_bw() + theme(aspect.ratio=1,  plot.title = element_text(hjust = 0.5)) + xlab("Soft Threshold (power)") + ylab("Scale Free Topology Model Fit,signed R^2") + ggtitle("Scale independence")
